Manuscript Figures

### 2021-09-16 src/manuscript_figures.Rmd
Update immunotherapy response analysis (add marker combination analysis)  and make cosmetic changes to some figures

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 8.27, fig.height = 11.69)
knitr::opts_knit$set(root.dir = params$workdir)
settings <- yaml::read_yaml(params$settings_file)
message(settings$GDCdataDir)
FigureFolder <- params$figures_folder
source(settings$utility_script)
library(data.table)
library(ggplot2)
library(pbapply)
library(ggrepel)
library(ggpubr)
library(cowplot)
library(ggridges)
library(ggcorrplot)
library(ComplexHeatmap)
library(pheatmap)
library(survminer)
library(survival)
library(caret)
library(treeheatr)
library(partykit)

@@

# performance visualisation - misclassified examples 
m <- as.matrix(table(res$maui_factors$pred, res$maui_factors$obs))
p2 <- pheatmap::pheatmap(apply(m, 1, function(x) round(x/sum(x) * 100, 1)), cluster_rows = F, cluster_cols = F, 
          silent = T, cellwidth = 10, cellheight = 10)

# plot cancer specific factors
M <- LFs$maui_factors$pancancer.cnv_gex_meth_mut
ct <- surv[match(rownames(M), bcr_patient_barcode)]$project

p3 <- plot_tsne(M, ct, show.labels = T) + 
  theme(legend.position = 'none')

@@

# data type contribution to top LF per factor
p5 <- plot_datatype_contribution_by_factor(LFs, FWs, 'maui_factors', 
                                           'pancancer', 'cnv_gex_meth_mut', factors = ct, 
                                           top_lfs = 1, top_features = 100) 
p5 <- p5 + labs(y = 'Relative Contribution\nto top latent factor') + 
  theme(legend.position = 'top', legend.background = element_blank(), 
        legend.title = element_blank())

@@

# combine plots for main figure 
Fig <- plot_grid(plot_grid(p3, p5, nrow = 1, labels = c('A', 'B'),
                           rel_widths = c(2,1)), 
                  plot_grid(p6, p7, nrow = 1, labels = c('C', 'D')), 
                  nrow = 2,
                  rel_heights = c(2,1))

fig_count <- fig_count + 1
Figures[[fig_count]] <- Fig
fig.name <- paste0('Figure', fig_count, '.benchmarks.pdf')
names(Figures)[fig_count] <- fig.name
ggsave(file.path(FigureFolder, fig.name),
              plot = Fig, units = 'in', width = 12, height = 12)
Legends[[fig_count]] <- " A) tSNE plot of MAUI latent factors learned from pan-cancer dataset  B) Percentage of top feature types contributing to top predictive maui latent factor per cancer type. C, D) Comparison of unsupervised clustering performances based on cluster homogeneity (Silhouette) in C and cluster stability (Average Proportion of Non-Overlap (APN) in D. Each point represents a clustering score for 132 k-means clustering results (21 cancer types x for 6 different values of k from 3 to 8) for each tool."

# supplementary figure

supFig <- cowplot::plot_grid(cowplot::plot_grid(p1, p2$gtable, nrow = 1, 
                                                labels = c('A', 'B'), rel_widths = c(1.2, 2)), 
                          p4, nrow = 2, labels = c('', 'C'), rel_heights = c(1.2, 2))
# print p3 to supplements 
supFig_count <- supFig_count + 1
SuppFigures[[supFig_count]] <- supFig
fig.name <- paste0('SuppFigure', supFig_count, '.benchmarks.supp.pdf')
names(SuppFigures)[supFig_count] <- fig.name
ggsave(file.path(FigureFolder, fig.name), 
              plot = supFig, units = 'in', width = 8.27, height = 11.69)
SuppLegends[[supFig_count]] <- "A) Predictive power of latent factors in distinguishing cancer types comparing MAUI with PCA/MOFA/MCIA. Mean Balanced Accuracy computed on the test dataset (30% of held-out data) trained on 70% of the dataset using an Elastic Net multi-class model. B) Confusion matrix of predicted versus true labels of samples' cancer types. The color of each cell represents the percentage of samples from the cancer type in the rows that are classified into the cancer types on the column. Cells that deviate from the red color represent relatively lower
level of classification accuracy. C) Top maui LFs detected per cancer type. Size/color/opacity of the points represent the average neural activation value of the LF for the corresponding cancer type samples."

```

@@

## 1. clinical factor associated MAUI LFs
# Find maui LFs associated to clinical factors and plot them

experiments <- grep('^TCGA-.*.cnv_gex_meth_mut', names(LFs$maui_factors), value = T)
# find clinical-factor associated LFs 
cl <- parallel::makeCluster(10)
parallel::clusterExport(cl, varlist = c('experiments', 'LFs', 'settings'))
clin.stats <- do.call(rbind, 
        pbapply::pbsapply(cl = cl, simplify = F, 
               experiments, function(experiment) {
               require(data.table)
               source(settings$utility_script)
               M <- LFs$maui_factors[[experiment]]
               clin <- process_clinical_covariates(rownames(M))
               dt <- do.call(rbind, 
                    pbapply::pbsapply(simplify = F, 
                                      colnames(clin), function(x) {
                      if(!is.numeric(clin[,x])) {
                        factors <- clin[,x]
                        m <- M[!is.na(factors),]
                        factors <- factors[!is.na(factors)]
                        dt <- get_factor_specific_variables(m, factors) 
                        dt$label <- x
                        return(dt)
                      }
                      return(NULL)
                      }))
               dt$project <- unlist(strsplit(experiment, "\\."))[[1]]
               return(dt)
             }))
parallel::stopCluster(cl)

@@

dt <- melt(ci, id.vars = 'project')
dt$variable <- ifelse(dt$variable == 'base', 'Only clinical factors', 'Clinical factors + MAUI LFs')

p2 <- ggplot(ci, aes(x = reorder(project, with_lf))) + 
  geom_segment(aes(x = reorder(project, with_lf), xend = project, 
                   y = base, yend = with_lf)) + 
  geom_point(data = dt, aes(x = project, y = value, color = variable), size = 2) +
  coord_flip() + 
  labs(x = '', y = '') + 
  theme(legend.title = element_blank(), legend.position = 'bottom', 
        legend.background = element_blank(), 
        legend.margin = margin(), 
        legend.direction = 'vertical', legend.box.background = element_blank()) +
  scale_color_brewer(type = 'qual', palette = 6)

@@

fig_count <- fig_count + 1
Figures[[fig_count]] <- Fig
fig.name <- paste0('Figure', fig_count, '.clinical_factors.pdf')
names(Figures)[fig_count] <- fig.name
ggsave(filename = file.path(FigureFolder, fig.name), 
       plot = Fig, width = 8.27, height = 11.69, units = 'in')
Legends[[fig_count]] <- "A) Top significant (padj < 0.05) clinical factor-associated LFs per cancer type. B) Harrell’s C-index for progression-free survival prediction accuracy computed using only clinical factors (tumor stage + age + gender) or using clinical factors along with survival-predictive MAUI LFs."

@@

```{r immunotherapy_response}
# immunotherapy response prediction analysis: 
# TODO: pass paths via args
settings_imtrp <- yaml::read_yaml('/data/local/buyar/arcas/pancancer_multiomics_manuscript/results/immunotherapy_response/Mariathasan_et_al/settings.yaml')

@@

# heatmap of top vars 
# plot maui factors for responders/non-responders
M <- LFs_imtrp$maui_factors$mariathasan.gex
top_vars <- unique(dt[tool == 'MAUI'][padj < 0.01]$variable)
m <- M[,top_vars]
f <- ifelse(colData$binaryResponse == 'CR/PR', 'Responders', 'Non-responders')
m <- m[!is.na(f),]
f <- f[!is.na(f)]
p2 <- pheatmap::pheatmap(get_basis_matrix(m[,top_vars], f), silent = T)

# survival stratification using the top LF 
require(survminer)
require(survival)
top_lf <- dt[order(padj)][ref_cl == 'Responders'][1,]$variable
cp <- find_survival_cutpoint(m[,top_lf,drop = F], colData, event_col = 'censOS', duration_col = 'os')
p3 <- plot_survival(surv = colData, 
                    partition.df = data.frame('group' = ifelse(m[,top_lf] > cp, 
                                              paste0(top_lf, ">", round(cp, 1)),
                                              paste0(top_lf, "<=", round(cp, 1))), 
                                              row.names = rownames(m)), 
                    duration_col = 'os', event_col = 'censOS')

# correlation of top LF with tumor mutation burden
# get samples with both response and tmb annotation
dt <- do.call(rbind, lapply(names(LFs_imtrp), function(tool) {
  M <- LFs_imtrp[[tool]]$mariathasan.gex
  dt <- data.table(cor(M, colData$`Neoantigen burden per MB`, use = 'complete.obs'),
                   keep.rownames = T)
  dt$tool <- tool
  return(dt)
}))
dt <- dt[,.SD[which.max(abs(V1))], by = c('tool')]
dt$tool <- toupper(gsub("_factors", "", dt$tool))
p4 <- ggplot(dt, aes(x = tool, y = abs(V1))) + 
  geom_bar(stat = 'identity', aes(fill = tool), position = 'dodge') +
  coord_flip() + 
  labs(y = 'Correlation with Tumor Mutation Burden') + 
  theme(legend.title = element_blank(), axis.title.y = element_blank(), 
        plot.title = element_text(hjust = 0.5)) 
# immune phenotypes 
dt <- do.call(rbind, lapply(names(LFs_imtrp), function(tool) {
  M <- LFs_imtrp[[tool]]$mariathasan.gex
  # find LFs predictive of immune phenotypes 
  dt <- get_factor_specific_variables(M, colData$`Immune phenotype`)[order(padj)]
  dt$tool <- tool
  return(dt)
}))

dt[,.SD[which.min(padj)],by = c('ref_cl', 'tool')]
dt$tool <- toupper(gsub("_factors", "", dt$tool))
p5 <- ggplot(dt[,.SD[which.min(padj)],by = c('ref_cl', 'tool')], 
             aes(x = ref_cl, y = -log10(padj))) + 
  geom_bar(stat = 'identity', aes(fill = tool), position = 'dodge') +
  geom_hline(yintercept = -log10(0.05)) + 
  labs(x = 'Tumor Immune Phenotypes') + 
  coord_flip() + 
  theme(legend.title = element_blank(), axis.title.y = element_blank(), 
        plot.title = element_text(hjust = 0.5))

Fig <- cowplot::plot_grid(
  cowplot::plot_grid(p1, p4, p5, nrow = 1, labels = 'AUTO'),
  cowplot::plot_grid(p2$gtable, p3$plot, nrow = 1, labels = c('D', 'E')),
  nrow = 2, 
  rel_heights = c(1,2)
  ) 
fig_count <- fig_count + 1
Figures[[fig_count]] <- Fig
fig.name <- paste0('Figure', fig_count, '.immunotherapy_response.pdf')
names(Figures)[fig_count] <- fig.name
ggsave(filename = file.path(FigureFolder, fig.name), 
       plot = Fig, units = 'in', 
       width = 12, height = 14)
Legends[[fig_count]] <- "Predicting responders to anti-PD-L1 treatment in a cohort of Metastatic Urothelial
Cancers (N=348) using MAUI. A) Comparison of top latent factors predictive of complete/partial response (CR/PR) to the anti-PD-L1. B) Comparison of top latent factors with respect to their correlation with tumor mutation burden status of the samples in the cohort C) Comparison of top latent factors predictive of immune phenotypes (inflamed/excluded/desert). D) Top MAUI LFs predictive of response to anti-PD-L1 response groups. E) Survival stratification of the cohort based activation score of LF44 (high = LF44 > 1.4, low = LF44 < 1.4)."
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, 
                      fig.width = 9, fig.height = 11)
knitr::opts_knit$set(root.dir = params$workdir)
settings <- yaml::read_yaml(params$settings_file)
message(settings$GDCdataDir)
FigureFolder <- params$figures_folder
source(settings$utility_script)
library(data.table)
library(ggplot2)
library(pbapply)
library(ggrepel)
library(ggpubr)
library(cowplot)
library(ggridges)
library(ggcorrplot)
library(ComplexHeatmap)
library(pheatmap)
library(survminer)
library(survival)
library(caret)
library(treeheatr)
library(partykit)

@@

# performance visualisation - misclassified examples 
m <- as.matrix(table(res$maui_factors$pred, res$maui_factors$obs))
# compute percentage of correct predictions
hm <- apply(m, 1, function(x) round(x/sum(x) * 100))
hm_labels <- hm
hm_labels[hm_labels < 2] <- '' #don't display very low values
p2 <- pheatmap::pheatmap(hm, cluster_rows = F, cluster_cols = F, 
          silent = T, cellwidth = 10, cellheight = 10, color = colorRampPalette(c('white', 'red'))(10), 
          display_numbers = hm_labels, fontsize = 8)

# plot cancer specific factors
M <- LFs$maui_factors$pancancer.cnv_gex_meth_mut
ct <- surv[match(rownames(M), bcr_patient_barcode)]$project
dt <- get_factor_specific_variables(M, ct)[padj < 0.05][order(padj)]
top_vars <- get_top_by_label(dt, 'ref_cl', topN = 5)

p3 <- plot_tsne(M[,unique(top_vars$variable)], ct, show.labels = T) + 
  theme(legend.position = 'none')

@@

# data type contribution to top LF per factor
p5 <- plot_datatype_contribution_by_factor(LFs, FWs, 'maui_factors', 
                                           'pancancer', 'cnv_gex_meth_mut', factors = ct, 
                                           top_lfs = 1, top_features = 500) 
p5 <- p5 + labs(y = 'Relative Contribution\nto top latent factor') + 
  theme(legend.position = 'right', legend.direction = 'vertical', 
        legend.background = element_blank(), 
        legend.title = element_blank(), legend.box.just = 'left')

@@

# combine plots for main figure 
Fig <- plot_grid(plot_grid(p3, p5, nrow = 1, labels = c('A', 'B'),
                           rel_widths = c(2,1.5)), 
                  plot_grid(p6, p7, 
                            nrow = 1, labels = c('C','D')), 
                  nrow = 2,
                  rel_heights = c(2,1))

fig_count <- fig_count + 1
Figures[[fig_count]] <- Fig
fig.name <- paste0('Figure', fig_count, '.benchmarks.pdf')
names(Figures)[fig_count] <- fig.name
ggsave(file.path(FigureFolder, fig.name),
              plot = Fig, units = 'in', width = 12, height = 12)
Legends[[fig_count]] <- " A) tSNE plot of MAUI latent factors (using top 5 latent factors enriched per cancer type) learned from pan-cancer dataset  B) Percentage of top feature types contributing to top predictive maui latent factor per cancer type. C, D) Comparison of unsupervised clustering performances based on cluster homogeneity (Silhouette) in C and cluster stability (Average Proportion of Non-Overlap (APN) in D. Each point represents a score for an individual clustering experiment in a total of 132 k-means clustering experiments (21 cancer types x for 6 different values of k from 3 to 8) for each tool."

# supplementary figure
supFig <- cowplot::plot_grid(cowplot::plot_grid(p1, p2$gtable, nrow = 1, 
                                                labels = c('A', 'B'), rel_widths = c(1.2, 2)), 
                          p4, nrow = 2, labels = c('', 'C'), rel_heights = c(1.2, 2))
# print p3 to supplements 
supFig_count <- supFig_count + 1
SuppFigures[[supFig_count]] <- supFig
fig.name <- paste0('SuppFigure', supFig_count, '.benchmarks.supp.pdf')
names(SuppFigures)[supFig_count] <- fig.name
ggsave(file.path(FigureFolder, fig.name), 
              plot = supFig, units = 'in', width = 8.27, height = 11.69)
SuppLegends[[supFig_count]] <- "A) Predictive power of latent factors in distinguishing cancer types comparing MAUI with PCA/MOFA/MCIA. Mean Balanced Accuracy computed on the test dataset (30% of held-out data) trained on 70% of the dataset using an Elastic Net multi-class model. B) Confusion matrix of predicted versus true labels of samples' cancer types. The color of each cell represents the percentage of samples from the cancer type in the rows that are classified into the cancer types on the column. Cells that deviate from the red color represent relatively lower
level of classification accuracy. C) Top maui LFs detected per cancer type. Size/color/opacity of the points represent the average neural activation value of the LF for the corresponding cancer type samples."
```

@@

## 1. clinical factor associated MAUI LFs
# Find maui LFs associated to clinical factors and plot them
experiments <- grep('^TCGA-.*.cnv_gex_meth_mut', names(LFs$maui_factors), value = T)
# find clinical-factor associated LFs 
cl <- parallel::makeCluster(10)
parallel::clusterExport(cl, varlist = c('experiments', 'LFs', 'settings'))
clin.stats <- do.call(rbind, 
        pbapply::pbsapply(cl = cl, simplify = F, 
               experiments, function(experiment) {
               require(data.table)
               source(settings$utility_script)
               M <- LFs$maui_factors[[experiment]]
               clin <- process_clinical_covariates(rownames(M))
               dt <- do.call(rbind, 
                    pbapply::pbsapply(simplify = F, 
                                      colnames(clin), function(x) {
                      if(!is.numeric(clin[,x])) {
                        factors <- clin[,x]
                        m <- M[!is.na(factors),]
                        factors <- factors[!is.na(factors)]
                        dt <- get_factor_specific_variables(m, factors) 
                        dt$label <- x
                        return(dt)
                      }
                      return(NULL)
                      }))
               dt$project <- unlist(strsplit(experiment, "\\."))[[1]]
               return(dt)
             }))
parallel::stopCluster(cl)

@@

dt <- melt(ci, id.vars = 'project')
dt$variable <- ifelse(dt$variable == 'base', 'Age+gender+stage', 'Age+gender+stage + MAUI LFs')

p2 <- ggplot(ci, aes(x = reorder(project, with_lf))) + 
  geom_segment(aes(x = reorder(project, with_lf), xend = project, 
                   y = base, yend = with_lf)) + 
  geom_hline(yintercept = c(0.5, 0.6, 0.7), linetype = 2) + 
  geom_point(data = dt, aes(x = project, y = value, color = variable), size = 2) +
  coord_flip() + 
  labs(x = '', y = '') + 
  theme(legend.title = element_blank(), legend.position = 'bottom', 
        legend.background = element_blank(), 
        legend.margin = margin(), 
        legend.direction = 'vertical', legend.box.background = element_blank()) +
  scale_color_brewer(type = 'qual', palette = 6)

@@

fig_count <- fig_count + 1
Figures[[fig_count]] <- Fig
fig.name <- paste0('Figure', fig_count, '.clinical_factors.pdf')
names(Figures)[fig_count] <- fig.name
ggsave(filename = file.path(FigureFolder, fig.name), 
       plot = Fig, width = 8.27, height = 11.69, units = 'in')
Legends[[fig_count]] <- "A) Top significant (padj < 0.05) clinical factor-associated LFs per cancer type. B) Harrell’s C-index for progression-free survival prediction accuracy computed using only clinical factors (age + gender + tumor stage) or using clinical factors along with survival-predictive MAUI LFs."

@@

```{r immunotherapy_response}
# immunotherapy response prediction analysis: 
# TODO: pass paths via args
projDir <- '/data/local/buyar/arcas/pancancer_multiomics_manuscript/results/immunotherapy_response/Mariathasan_et_al'
settings_imtrp <- yaml::read_yaml(file.path(projDir, 'settings.yaml'))
gex_all <- readRDS(file.path(projDir, 'mariathasan.gex.all_genes.normalised.RDS'))
human_gene_signatures <- readRDS(file.path(projDir, 'human_gene_signatures.RDS'))

@@

# correlation of top LF with tumor mutation burden
# get samples with both response and tmb annotation
dt <- do.call(rbind, lapply(names(LFs_imtrp), function(tool) {
  M <- LFs_imtrp[[tool]]$mariathasan.gex
  dt <- data.table(cor(M, colData$`Neoantigen burden per MB`, use = 'complete.obs'),
                   keep.rownames = T)
  dt$tool <- tool
  return(dt)
}))
dt <- dt[,.SD[which.max(abs(V1))], by = c('tool')]
dt$tool <- toupper(gsub("_factors", "", dt$tool))
p2 <- ggplot(dt, aes(x = tool, y = abs(V1))) + 
  geom_bar(stat = 'identity', aes(fill = tool), position = 'dodge') +
  coord_flip() + 
  labs(y = 'Correlation with Tumor Mutation Burden') + 
  theme(legend.position = 'none', axis.title.y = element_blank(), 
        plot.title = element_text(hjust = 0.5)) 
# immune phenotypes 
dt <- do.call(rbind, lapply(names(LFs_imtrp), function(tool) {
  M <- LFs_imtrp[[tool]]$mariathasan.gex
  # find LFs predictive of immune phenotypes 
  dt <- get_factor_specific_variables(M, colData$`Immune phenotype`)[order(padj)]
  dt$tool <- tool
  return(dt)
}))

dt[,.SD[which.min(padj)],by = c('ref_cl', 'tool')]
dt$tool <- toupper(gsub("_factors", "", dt$tool))
p3 <- ggplot(dt[,.SD[which.min(padj)],by = c('ref_cl', 'tool')], 
             aes(x = ref_cl, y = -log10(padj))) + 
  geom_bar(stat = 'identity', aes(fill = tool), position = 'dodge') +
  geom_hline(yintercept = -log10(0.05)) + 
  labs(x = 'Tumor Immune Phenotypes') + 
  coord_flip() + 
  theme(legend.title = element_blank(), axis.title.y = element_blank(), 
        plot.title = element_text(hjust = 0.5))

# test comparison of maui LFs and published markers from Mariathasan et al
# in terms of response prediction
# published markers from Mariathasan et al (https://www.nature.com/articles/nature25501#Sec4)
# 1. TMB (tumor neoantigen burden) 2. CD8 effector T cell markers (8 genes)
# 3. F-TBRS: fibroblast tgf-beta response signature (4 genes see https://www.nature.com/articles/nature25501/figures/3)

# find top maui LFs informative for response prediction 
M <- scale(LFs_imtrp$maui_factors$mariathasan.gex)
labels <- colData[match(rownames(M), colData$bcr_patient_barcode),]$binaryResponse
df <- cbind(data.frame(M), 'y' = labels)
df <- df[!is.na(df$y),]
df$y <- as.factor(df$y)
# build an initial glmnet model using all LFs on training data
fit <- predict_categorical(df, 'CR/PR') 
# get subset of top LFs 
v <- caret::varImp(fit)[['importance']]
top_lfs <- data.table(v, keep.rownames = T)[order(Overall, decreasing = T)][Overall > 0]$rn

# make a heatmap of top predictive lfs 
m <- as.matrix(df[,-ncol(df)])
f <- ifelse(df$y == 'CR/PR', 'Responders', 'Non-responders')
p4 <- pheatmap::pheatmap(get_basis_matrix(m[,top_lfs], f), silent = T, cellheight = 50, cluster_rows = F)

# survival stratification using the top LF 
require(survminer)
require(survival)
top_lf <- top_lfs[1]
cp <- find_survival_cutpoint(m[,top_lf,drop = F], colData, event_col = 'censOS', duration_col = 'os')
p5 <- plot_survival(surv = colData, 
                    partition.df = data.frame('group' = ifelse(m[,top_lf] > cp, 
                                              paste0(top_lf, ">", round(cp, 1)),
                                              paste0(top_lf, "<=", round(cp, 1))), 
                                              row.names = rownames(m)), 
                    duration_col = 'os', event_col = 'censOS')

# get the assay data for the studied markers for CD8 effectors + TBRS etc.
signatures <- list('cd8_Teff' = human_gene_signatures$`CD 8 T effector`, 
                   'F_TBRS' = c('ACTA2', 'COL4A1', 'TAGLN', 'SH3PXD2A'))
# make a data frame of marker genes + TMB measures + top MAUI LFs
DF <- merge(data.frame(t(gex_all[unlist(signatures),])), 
            data.frame(M[,top_lfs]), by = 'row.names')
DF$TMB <- colData[match(DF$Row.names, colData$bcr_patient_barcode),]$`Neoantigen burden per MB`
# response variable
DF$y <- colData[match(DF$Row.names, colData$bcr_patient_barcode),]$binaryResponse
# remove samples without response variable
DF <- DF[!is.na(DF$y),]
# remove samples without TMB values 
DF <- DF[!is.na(DF$TMB),]
DF <- data.frame(DF[,-1], row.names = DF$Row.names)
DF$y <- as.factor(DF$y)

L <- list('TMB' = 'TMB',
          'MAUI' = top_lfs, 
          'CD8_Teff + F_TBRS' = c(signatures$cd8_Teff, signatures$F_TBRS))
# now predict response using subsets of features 
# get combination of models
combs <- c(asplit(combn(names(L), 2), 2),
           asplit(combn(names(L), 3), 2), 
           'MAUI',
           'CD8_Teff + F_TBRS')
results <- do.call(rbind, lapply(combs, function(x) {
  comb <- paste0(x, collapse = " + ")
  message("trying combination:",comb)
  included <- as.vector(unlist(L[x]))  # variables included in the model
  message("including variables:",paste(included, collapse = ' '))
  res <- predict_cluster_labels_glmnet(scale(as.matrix(DF[,intersect(colnames(DF), included),drop = F])), 
                                DF$y, repeats = 5, sampling = 'down')
  res$comb <- comb
  return(res)
}))

results$comb <- stringr::str_wrap(results$comb, width = 12)
p6 <- ggplot(results[order(auc)][label == 'CR/PR'], 
       aes(x = reorder(comb, -auc), y = auc)) + 
  geom_bar(stat = 'identity', aes(fill = auc)) + 
  geom_errorbar(aes(ymin = auc.lower, ymax = auc.upper), stat = 'identity', 
                width = 0.1) + 
  labs(x = 'Marker Combination', y = 'AUC') + 
  theme(legend.position = 'none', axis.text.x = element_text(angle = 30, hjust = 1))

p5 <- p5$plot + theme(legend.title = element_blank(), legend.direction = 'vertical')
Fig <- cowplot::plot_grid(
  cowplot::plot_grid(p1, p3, p2, nrow = 1, labels = c('A', 'B', 'C')), 
  cowplot::plot_grid(p5, p4$gtable, nrow = 1, labels = c('D', 'E')), 
  cowplot::plot_grid(cowplot::ggdraw(), p6, cowplot::ggdraw(), rel_widths = c(1, 5, 1), nrow = 1, labels = c('', 'F', '')), 
  nrow = 3
)
fig_count <- fig_count + 1
Figures[[fig_count]] <- Fig
fig.name <- paste0('Figure', fig_count, '.immunotherapy_response.pdf')
names(Figures)[fig_count] <- fig.name
ggsave(filename = file.path(FigureFolder, fig.name), 
       plot = Fig, units = 'in', 
       width = 12, height = 14)
Legends[[fig_count]] <- "Predicting responders to anti-PD-L1 treatment in a cohort of Metastatic Urothelial
Cancers (N=216) using MAUI. A) Comparison of top latent factors predictive of complete/partial response (CR/PR) to the anti-PD-L1. B) Comparison of top latent factors predictive of immune phenotypes (inflamed/excluded/desert). C)  Comparison of top latent factors with respect to their correlation with tumor mutation burden status of the samples in the cohort D) Survival stratification of the cohort based activation score of top MAUI latent factor E) Average value of top MAUI LFs predictive of response to anti-PD-L1 response groups.
F) Comparison of marker combinations in terms of accuracy in predicting anti-PD-L1 response. TMB: tumor mutation burden, 
CD8_Teff: 12 gene signature for CD8+ effector T-cells, F_TBRS: 4-gene pan-fibroblast TGFβ response signature, MAUI: top predictive MAUI LFs as seen in panel E). Each bar plot represents prediction accuracy (AUC) when using the corresponding subset of variables in an Elastic Net model."
```
